### 2023-07-03 manuscript.tex
Add submitted version to header [ci skip]
This build is based on
https://github.com/habi/EAWAG-manuscript/commit/0dada243d2d4e03345245209804557977c66c438.

This commit was created by the following CI build and job:
https://github.com/habi/EAWAG-manuscript/commit/0dada243d2d4e03345245209804557977c66c438/checks
https://github.com/habi/EAWAG-manuscript/actions/runs/5445961425

\emph{A preprint of this manuscript is available at bioRχiv with the \href{https://doi.org/10.1101/2023.03.30.534917}{doi:10.1101/2023.03.30.534917}.}
\emph{We submitted \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.0}{\texttt{v1.0}} (\href{https://habi.github.io/EAWAG-manuscript/v/e1e2ef76a476174a4115937d77457037ddec95df/}{online version}) of the manuscript to \href{https://journals.plos.org/plosone/}{PLOS ONE}.}
\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.0...ced46ab1b2fbda07ed353d379d6530b9405eee43}{has been updated} since submission.}

This manuscript
(\href{https://habi.github.io/EAWAG-manuscript/v/ced46ab1b2fbda07ed353d379d6530b9405eee43/}{permalink})
was automatically generated
from \href{https://github.com/habi/EAWAG-manuscript/tree/ced46ab1b2fbda07ed353d379d6530b9405eee43}{habi/EAWAG-manuscript@ced46ab}
on July 3, 2023.

>>>>

\emph{A preprint of this manuscript is available at bioRχiv with the \href{https://doi.org/10.1101/2023.03.30.534917}{doi:10.1101/2023.03.30.534917}.}
\emph{We submitted \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.0}{\texttt{v1.0}} (\href{https://habi.github.io/EAWAG-manuscript/v/e1e2ef76a476174a4115937d77457037ddec95df/}{online version}) of the manuscript to \href{https://journals.plos.org/plosone/}{PLOS ONE}.}
\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.0...0dada243d2d4e03345245209804557977c66c438}{has been updated} since submission.}

This manuscript
(\href{https://habi.github.io/EAWAG-manuscript/v/0dada243d2d4e03345245209804557977c66c438/}{permalink})
was automatically generated
from \href{https://github.com/habi/EAWAG-manuscript/tree/0dada243d2d4e03345245209804557977c66c438}{habi/EAWAG-manuscript@0dada24}
on July 3, 2023.
